Supplementary Information

### 2022-08-30 markdown/compile.Rmd
compile

\pagenumbering{gobble}
\pagebreak
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
library(systemfit)
library(kevostools)
library(AER)
library(sandwich)
library(lmtest)
library(scales)
library(ggpubr)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(data.table)
library(stargazer)
loadfonts()
```
\pagenumbering{arabic}
\doublespacing

```{r did-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time.rds")
print(p2)
```

```{r did-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time_no_prior.rds")
print(p2)
```

@@

@@

```{r coef-plot-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/coef_plot_no_prior.rds")
print(p2)
```

```{r event-study-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/event_study.rds")
print(p2)
```

@@

```{r black-overall-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Overall", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_overall_effect.rds")
print(p2)
```

```{r black-overall-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Overall (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_overall_effect_no_prior.rds")
print(p2)
```

```{r black-relative-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_relative_effect.rds")
print(p2)
```

```{r black-relative-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/black_relative_effect_no_prior.rds")
print(p2)
```

```{r non-black-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Nonblack", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/non_black_effect.rds")
print(p2)
```

```{r non-black-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Nonblack (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/non_black_effect_no_prior.rds")
print(p2)
```

```{r overall-time-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/overall_effect.rds")
print(p2)
```

```{r overall-time-no-prior, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Black Relative (no prior turnout in match)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/overall_effect_no_prior.rds")
print(p2)
```

>>>>

\pagenumbering{gobble}
\pagebreak
```{r setup, echo = F, message = F, warning = F}
library(ragg)
library(systemfit)
library(ggpubr)
library(tidyverse)
library(kableExtra)
library(data.table)
ragg_png = function(..., res = 300) {
  ragg::agg_png(..., res = res, units = "in")
}
knitr::opts_chunk$set(dev = "ragg_png", dpi = 800)
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf")
```
\pagenumbering{arabic}
\doublespacing

```{r did-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 8, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/stopped_any_time.rds")
p2
```

@@

```{r did-different-approaches, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 6, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/ts.rds")
print(p2)
```

@@

```{r event-study-primary, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 4, fig.cap = "\\label{fig:did-1}Effect of Being Ticketed on Turnout", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/event_study.rds")
print(p2)
```

@@

```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:did-1}Black Relative", fig.pos = "H", fig.align = "center"}
p2 <- readRDS("temp/window_plot_good.rds")
print(p2)
```

### 2022-08-30 markdown/compile.tex
compile

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact}
\author{}
\date{\vspace{-2.5em}May 04, 2022}

@@

{\centering \includegraphics{compile_files/figure-latex/did-no-prior-1}

\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:did-no-prior}
\end{figure}

@@

@@

{\centering \includegraphics{compile_files/figure-latex/coef-plot-no-prior-1}

\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no prior turnout in match)}\label{fig:coef-plot-no-prior}
\end{figure}

@@

{\centering \includegraphics{compile_files/figure-latex/black-overall-primary-1}

@@

\caption{\label{fig:did-1}Black Overall}\label{fig:black-overall-primary}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/black-overall-no-prior-1}

\caption{\label{fig:did-1}Black Overall (no prior turnout in match)}\label{fig:black-overall-no-prior}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/black-relative-primary-1}

\caption{\label{fig:did-1}Black Relative}\label{fig:black-relative-primary}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/black-relative-no-prior-1}

\caption{\label{fig:did-1}Black Relative (no prior turnout in match)}\label{fig:black-relative-no-prior}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/non-black-primary-1}

\caption{\label{fig:did-1}Nonblack}\label{fig:non-black-primary}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/non-black-no-prior-1}

\caption{\label{fig:did-1}Nonblack (no prior turnout in match)}\label{fig:non-black-no-prior}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/overall-time-primary-1}

\caption{\label{fig:did-1}Black Relative}\label{fig:overall-time-primary}
\end{figure}

{\centering \includegraphics{compile_files/figure-latex/overall-time-no-prior-1}

\caption{\label{fig:did-1}Black Relative (no prior turnout in match)}\label{fig:overall-time-no-prior}
\end{figure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Ticketing and Turnout: The Participatory Consequences of Low-Level Police Contact}
\author{}
\date{\vspace{-2.5em}June 16, 2022}

@@

@@

{\centering \includegraphics{compile_files/figure-latex/did-different-approaches-1}

\caption{\label{fig:did-1}Effect of Being Ticketed on Turnout (no matching at all)}\label{fig:did-different-approaches}
\end{figure}

@@

@@

{\centering \includegraphics{compile_files/figure-latex/windows-1}

@@

\caption{\label{fig:did-1}Black Relative}\label{fig:windows}
\end{figure}

### 2022-08-30 markdown/si.Rmd
compile

j <- table %>% 
  mutate_all(linebreak) %>% 
  knitr::kable(booktabs = T, caption = "(\\#tab:change-dobs) Results of Shifting Birthdates", linesep = "", escape = F,
               col.names = linebreak(c("Group", "Number of Matches Between\nTraffic Stop and Voter File Records")),
               align = "c") %>% 
  kable_styling(latex_options = c("HOLD_position"),
                position = "center")
j
```
\end{singlespace}

@@

# Sensitivity to Narrower Windows

In the individual-level section of this manuscript, voters stopped in the 2 years prior to an election are considered treated, and we draw our controls from the voters stopped 2 years after the election. It is perhaps the case that this large window results in implausible matches; under this design, a treated voter stopped in December of 2012 could draw a control not stopped until October of 2016. Voters stopped nearly 4 years apart from one another might differ in meaningful ways that our matching models cannot capture.

Here, we re-run our matching process on a variety of different windows around the elections. In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, until reaching the two-years used in the manuscript.

Figure 1 shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election. As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls). As such, the confidence interval shrinks, but the treated and control voters are stopped at more distant temporal points from one another. The left-most side of the plot shows that the overall effect is robust to very strict assumptions. In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.

```{r windows, echo = FALSE, message = F, warning = F, fig.width = 7.5, fig.height = 5, fig.cap = "\\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows", fig.pos = "!htb", fig.align = "center"}
p2 <- readRDS("temp/windows_rob.rds")
print(p2)
```

>>>>

j <- table %>% 
  mutate_all(linebreak) %>% 
  knitr::kable(booktabs = T, caption = "(\\#tab:change-dobs) Results of Shifting Birthdates", linesep = "", escape = F,
               col.names = linebreak(c("Group", "Number of Matches Between\nTraffic Stop and Voter File Records")),
               align = "c") %>% 
  kable_styling(latex_options = c("HOLD_position"),
                position = "center")
j

knitr::kable(table, booktabs = T, caption = "\\label{tab:change-dobs} Results of Shifting Birthdates", linesep = "", align=rep('c', ncol(table)), format = "latex",
               col.names = linebreak(c("Group", "Number of Matches Between Traffic Stop and Voter File Records"))) %>%
  kable_styling(font_size = 10,
                latex_options = c("HOLD_position")) %>%
  column_spec(c(1), width = "5cm") %>% 
  column_spec(c(2), width = "6cm") %>% 
  save_kable(paste0("./temp/shift_tab.tex"))

```
\end{singlespace}

@@

### 2022-08-30 markdown/si.tex
compile

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary Information},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\pagenumbering{gobble}
\pagenumbering{arabic}
\doublespacing
\newpage

@@

Our models exploring the turnout effects of traffic stops in Hillsborough County, Florida, require that we merge administrative records using the identifiers in the data. This runs the risk of identifying false positives. To test the prevalence of false positives in our administrative matching procedure, we use the test developed by \protect\hyperlink{ref-Meredith2014}{Meredith and Morse} (\protect\hyperlink{ref-Meredith2014}{2014}). By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern. In Table 1 we begin by merging all names and dates of birth in the traffic stop data with the names and dates of birth in the Hillsborough County registered voter file. We then add and subtract 35 days from the birth dates in the traffic stop data. If there are no false positives, these records should match with no records from the registered voter file.

@@

\caption{\label{tab:shift-dobs-chunk}\label{tab:change-dobs} Results of Shifting Birthdates}
\centering
\begin{tabular}[t]{cc}
\toprule
Group & \makecell[c]{Number of Matches Between\\Traffic Stop and Voter File Records}\\
\midrule
Actual Birthdate & 263,152\\
Birthdate + 35 Days & 78\\
Birthdate - 35 Days & 60\\
\bottomrule
\end{tabular}
\end{table}
\end{singlespace}

@@

\hypertarget{sensitivity-to-narrower-windows}{%
\section{Sensitivity to Narrower Windows}\label{sensitivity-to-narrower-windows}}

In the individual-level section of this manuscript, voters stopped in the 2 years prior to an election are considered treated, and we draw our controls from the voters stopped 2 years after the election. It is perhaps the case that this large window results in implausible matches; under this design, a treated voter stopped in December of 2012 could draw a control not stopped until October of 2016. Voters stopped nearly 4 years apart from one another might differ in meaningful ways that our matching models cannot capture.

Here, we re-run our matching process on a variety of different windows around the elections. In the most conservative approach, we force voters stopped in the month before an election to match with voters stopped in the month after the election; we then gradually relax this assumption by allowing voters stopped in the 2 months before the election to match to those stopped in the 2 months afterwards, until reaching the two-years used in the manuscript.

Figure 1 shows that our overall treatment effect is remarkably consistent regardless of the size of the window drawn around the election. As we expand the window, we gain more treated voters (and treated voters have a larger pool of potential controls). As such, the confidence interval shrinks, but the treated and control voters are stopped at more distant temporal points from one another. The left-most side of the plot shows that the overall effect is robust to very strict assumptions. In each case, we are re-estimating our primary models in which the covariates used in the matching exercise are also included in the econometric model.

\begin{figure}[!htb]

{\centering \includegraphics{si_files/figure-latex/windows-1}

}

\caption{\label{fig:rob-window}Estimated Treatment Effect for Different Treatment Windows}\label{fig:windows}
\end{figure}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Meredith2014}{}%
Meredith, Marc, and Michael Morse. 2014. {``Do {Voting Rights Notification Laws Increase Ex-Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49. \url{https://doi.org/10.1177/0002716213502931}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary Information},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\pagenumbering{gobble}
\pagebreak

\doublespacing

@@

Our models exploring the turnout effects of traffic stops in Hillsborough County, Florida, require that we merge administrative records using the identifiers in the data. This runs the risk of identifying false positives. To test the prevalence of false positives in our administrative matching procedure, we use the test developed by Meredith and Morse (\protect\hyperlink{ref-Meredith2014}{2014}). By systematically permuting the birth dates in one set of records, we can see whether false positive matches are a major concern. In Table 1 we begin by merging all names and dates of birth in the traffic stop data with the names and dates of birth in the Hillsborough County registered voter file. We then add and subtract 35 days from the birth dates in the traffic stop data. If there are no false positives, these records should match with no records from the registered voter file.

@@

\caption{\label{tab:shift-dobs-chunk}\label{tab:change-dobs} Results of Shifting Birthdates}
\centering
\begin{tabular}[t]{cc}
\toprule
Group & \makecell[c]{Number of Matches Between\\Traffic Stop and Voter File Records}\\
\midrule
Actual Birthdate & 263,149\\
Birthdate + 35 Days & 78\\
Birthdate - 35 Days & 60\\
\bottomrule
\end{tabular}
\end{table}
\end{singlespace}

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Meredith2014}{}}%
Meredith, Marc, and Michael Morse. 2014. {``Do {Voting Rights Notification Laws Increase Ex-Felon Turnout}?''} \emph{The ANNALS of the American Academy of Political and Social Science} 651 (1): 220--49. \url{https://doi.org/10.1177/0002716213502931}.
